High Speed Object Tracking using Multiple Kernelized Correlation Filters

### 2017-03-31 draft.tex
Added .gitignore; revised the draft to outline the content

%%%%%%%%% BODY TEXT
\section{Introduction}
The tracking-by-detection methods have recently emerged as robust, powerful, and highly discriminative trackers replacing the preceding generative trackers that focused on only target modeling. Some of the recent tracking-by-detection algorithms are Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple Instance Learning \cite{babenko2009visual}, Correlation Filter based trackers \cite{bolme2010visual,henriques2015high}, and Struck \cite{hare2012efficient}. These tracking-by-detection methods train an object-specific classifier on the fly with the focus of discriminating the target from the background. Learning an object-specific classifier in an online manner can better handle challenging scenarios with the cost of increased complexity. In order to train a classifier, one need positive and negative samples. Randomly collecting negative samples from the background area can be one straightforward way of building training data to train the classifier. However, there can be two issues in this framework. First, the randomly collected samples can have large correlation resulting in a weak classifier. Also, such framework is not feasible for real-time tracking as the number of samples gradually increases. Most of the tracking-by-detection algorithms focus on efficient incremental update of a classifier together with more useful background sampling.

>>>>

%%%%%%%%% BODY TEXT
\section{Introduction}

A practical solution to target-following mode

\begin{itemize}
\item Introduction: Should talk about, at least, motivation of this
  work, brief review of the literature, and contribution
\item Method: Detail the method w.r.t. a diagram of system
  architecture or pseudo code
\begin{itemize}
\item Kernelized Correlation Filter
\item A variant of KCF: Multiple KCF w/ PF
\item Re-detection
\item Estimation of geometry between a target and a drone
\end{itemize}
\item Experiment: Detail the data, and experimental setup; results and findings
\item Conclusion
\end{itemize}

The tracking-by-detection methods have recently emerged as robust,
powerful, and highly discriminative trackers replacing the preceding
generative trackers that focused on only target modeling. Some of the
recent tracking-by-detection algorithms are
Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple
Instance Learning \cite{babenko2009visual}, Correlation Filter based
trackers \cite{bolme2010visual,henriques2015high}, and Struck
\cite{hare2012efficient}. These tracking-by-detection methods train an
object-specific classifier on the fly with the focus of discriminating
the target from the background. Learning an object-specific classifier
in an online manner can better handle challenging scenarios with the
cost of increased complexity. In order to train a classifier, one need
positive and negative samples. Randomly collecting negative samples
from the background area can be one straightforward way of building
training data to train the classifier. However, there can be two
issues in this framework. First, the randomly collected samples can
have large correlation resulting in a weak classifier. Also, such
framework is not feasible for real-time tracking as the number of
samples gradually increases. Most of the tracking-by-detection
algorithms focus on efficient incremental update of a classifier
together with more useful background sampling.
